Stage-Splitting a Modal Language

### 2014-09-26 paper/paper.tex
factored example section into its own file
reorganized splitting section
minor changes after meeting with nico
fix the issue with listings in footnotes
some text in section 3 about top-level operational semantics
adding colors to listings

\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{mathabx}
\usepackage{listings}
\usepackage{hyperref}

\usepackage{cleveref}
\AtBeginDocument{\renewcommand\ref\cref}
\crefname{figure}{Figure}{Figures}

@@

\lstset{language=ML,
        columns=fullflexible,
        basicstyle=\ttfamily,
        tabsize=4,
        escapeinside={"*}{*"},
        literate={|->}{{\ $\mapsto$\ }}1
                 {xhat}{{$\hat{\texttt{x}}$}}1
                 {yhat}{{$\hat{\texttt{y}}$}}1
                 {zhat}{{$\hat{\texttt{z}}$}}1
                 {$}{{$\fut$}}1}

@@

\authorinfo{Name1}
           {Affiliation1}
           {Email1}
\authorinfo{Name2\and Name3}
           {Affiliation2/3}
           {Email2/3}

@@

\vfill\eject\pagebreak
\input{splitting}

\input{relatedwork}

>>>>

\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{mathabx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{cprotect}

\usepackage{cleveref}
\AtBeginDocument{\renewcommand\ref\cref}
\crefname{figure}{Figure}{Figures}
\crefname{theorem}{Theorem}{Theorems}

@@

\lstset{language=ML,
        columns=fullflexible,
        basicstyle=\ttfamily,
        tabsize=4,
        escapeinside={"*}{*"},
        moredelim=*[is][\color{red}]{1`}{`},
        moredelim=*[is][\color{blue}]{2`}{`},
        literate={|->}{{\ $\mapsto$\ }}1
                 {xhat}{{$\hat{\texttt{x}}$}}1
                 {yhat}{{$\hat{\texttt{y}}$}}1
                 {zhat}{{$\hat{\texttt{z}}$}}1
                 {murec}{{$\mu$}}1
                 {alpha}{{$\alpha$}}1
                 {beta}{{$\beta$}}1
                 {$}{{$\fut$}}1}

@@

\authorinfo{Nicolas Feltman \and Carlo Angiuli \and Umut Acar \and Kayvon Fatahalian}
           {Carnegie Mellon University}
           {\{nfeltman,cangiuli,umut,kayvonf\}@cs.cmu.edu}

@@

\vfill\eject\pagebreak
\input{splitting}
\input{algoexamples}
\input{relatedwork}

### 2014-09-26 paper/semantics.tex
use minipage instead of deprecated subfigure (not in texlive 2014)
adding colors to listings

\begin{figure*}
\label{fig:quickselect}
\begin{subfigure}{0.5\textwidth}
\begin{lstlisting} 
datatype list = Empty | Cons of int * list
fun partition (p : int, l : list) 
  : (int*list*list) =
  case unroll l of 
    Empty => (0,Empty, Empty) 
  | Cons (h,t) =>
      let (s,left,right) = partition (p,t) in
      if h<p 
      then (s+1,Cons(h,left),right)
      else (s,left,Cons(h,right))

fun qs (l : list, i : int) : int = 
  case l of
    Empty => next {0}
  | Cons (h,t) => 
      let (left,right,n) = partition h t in
        case compare i n of
          LT => qs (left, i)
        | EQ => h
        | GT => qs (right, i-n-1)
\end{lstlisting}
\caption{Unstaged Code}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\begin{lstlisting} 
datatype list = Empty | Cons of int * list
fun partition (p : int, l : list) = ...

fun qs (l : list, i: $int) : $int = 
  case l of
    Empty => next {0}
  | Cons (h,t) => 
      let (left,right,n) = partition h t in
      next{
        let n = hold{n} in
          case compare prev{i} n of
            LT => prev {qs (left i)}
          | EQ => hold {h}
          | GT => prev {qs (right, next{prev{i}-n-1)}}
      }	
\end{lstlisting}
\caption{Staged Code}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\begin{lstlisting} 
datatype list = Empty | Cons of int * list
fun partition (p : int, l : list) = ...

@@

fun qs2 (p : tree, i : int) : int = 
  case unroll p of
    Leaf => 0
  | Branch (n,h,p1,p2) => 
      case compare i n of
        LT => qs2 (p1,i)
      | EQ => h
      | GT => qs2 (p2,i-n-1)
\end{lstlisting}
\caption{Split Code}
\end{subfigure}
\caption{Caption place holder}
\end{figure*}

>>>>

\begin{figure*}
\label{fig:quickselect}
\begin{minipage}{0.5\textwidth}
\begin{lstlisting} 
datatype list = Empty | Cons of int * list
fun partition (p : int, l : list) 
  : (int*list*list) =
  case unroll l of 
    Empty => (0,Empty, Empty) 
  | Cons (h,t) =>
      let (s,left,right) = partition (p,t) in
      if h<p 
      then (s+1,Cons(h,left),right)
      else (s,left,Cons(h,right))

fun qs (l : list, i : int) : int = 
  case l of
    Empty => next {0}
  | Cons (h,t) => 
      let (left,right,n) = partition h t in
        case compare i n of
          LT => qs (left, i)
        | EQ => h
        | GT => qs (right, i-n-1)
\end{lstlisting}
\caption{Unstaged Code}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\begin{lstlisting} 
datatype list = Empty | Cons of int * list
fun partition (p : int, l : list) = ...

fun qs (l : list, i: $int) : $int = 
  case l of
    1`Empty` => next {2`0`}
  | Cons (h,t) => 
      let (left,right,n) = partition h t in
      next{
        let n = hold{n} in
          case compare prev{i} n of
            LT => prev {qs (left i)}
          | EQ => hold {h}
          | GT => prev {qs (right, next{prev{i}-n-1)}}
      }	
\end{lstlisting}
\caption{Staged Code}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\begin{lstlisting} 
datatype list = Empty | Cons of int * list
fun partition (p : int, l : list) = ...

@@

fun qs2 (p : tree, i : int) : int = 
  case unroll p of
    Leaf => 0
  | Branch (n,h,p1,p2) => 
      case compare i n of
        LT => qs2 (p1,i)
      | EQ => h
      | GT => qs2 (p2,i-n-1)
\end{lstlisting}
\caption{Split Code}
\end{minipage}
\caption{Caption place holder}
\end{figure*}
